---
title: "All Breed Concerned By Meat Index"
author: "Peter von Rohr and Sophie Kunz"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
vignette: >
  %\VignetteIndexEntry{All Breed Concerned By Meat Index}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r, include=FALSE}
library(dplyr)
```


#1. Computing Economic Value

```{r, include=FALSE}
l_gen_sd <- list(CCc = 0.6336,
                 CCa = 0.6335,
                 CFc = 0.3474,
                 CFa = 0.3609,
                 CWc = 0.0557,
                 CWa = 0.1395)
```

##Carcass conformation adults (CCa)
```{r}
### # prices
vec_price_cca <- c(7.526960,7.938872,8.450784,8.800000,9.137304,9.392693,9.642693)
```

```{r, include=FALSE}
n_mean_cca_ob <- 5.20
n_sd_cca_ob <- 1.02
vec_count_cca_ob <- c(4,43,218,1150,2106,1905,522)
vec_freq_cca_ob <- vec_count_cca_ob / sum(vec_count_cca_ob)
```

```{r, include=FALSE}
(ev_cca_ob <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cca_ob,
                        pn_sd = n_sd_cca_ob,
                        pvec_class_freq = vec_freq_cca_ob,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_cca,
                        pn_delta_mean = .1,
                        pn_gen_sd = l_gen_sd$CCa,
                        pb_verbose = TRUE))
```

```{r, include=FALSE}
n_mean_cca_bv <- 4.78
n_sd_cca_bv <- 1.27
vec_count_cca_bv <- c(273,1562,5982,17808,14303,11438,5875)
vec_freq_cca_bv <- vec_count_cca_bv / sum(vec_count_cca_bv)

```

```{r, include=FALSE}
(ev_cca_bv <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cca_bv,
                        pn_sd = n_sd_cca_bv,
                        pvec_class_freq = vec_freq_cca_bv,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_cca,
                        pn_delta_mean = .1,
                        pn_gen_sd = l_gen_sd$CCa,
                        pb_verbose = TRUE))
```

```{r, include=FALSE}
n_mean_cca_si <- 5.83
n_sd_cca_si <- 0.9
vec_count_cca_si <- c(4,38,377,3994,13917,24738,13535)
vec_freq_cca_si <- vec_count_cca_si / sum(vec_count_cca_si)
```

```{r, include=FALSE}
(ev_cca_si <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cca_si,
                        pn_sd = n_sd_cca_si,
                        pvec_class_freq = vec_freq_cca_si,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_cca,
                        pn_delta_mean = .1,
                        pn_gen_sd = l_gen_sd$CCa,
                        pb_verbose = TRUE))
```

```{r, include=FALSE}
n_mean_cca_sf <- 4.57
n_sd_cca_sf <- 1.18
vec_count_cca_sf <- c(165,1189,4814,11545,10445,6303,1755)
vec_freq_cca_sf <- vec_count_cca_sf / sum(vec_count_cca_sf)
```

```{r, include=FALSE}
(ev_cca_sf <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cca_sf,
                        pn_sd = n_sd_cca_sf,
                        pvec_class_freq = vec_freq_cca_sf,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_cca,
                        pn_delta_mean = .1,
                        pn_gen_sd = l_gen_sd$CCa,
                        pb_verbose = TRUE))
```

```{r, include=FALSE}
n_mean_cca_mo <- 5.39
n_sd_cca_mo <- 0.94
vec_count_cca_mo <- c(10,33,194,1341,3511,3730,979)
vec_freq_cca_mo <- vec_count_cca_mo / sum(vec_count_cca_mo)
```

```{r, include=FALSE}
(ev_cca_mo <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cca_mo,
                        pn_sd = n_sd_cca_mo,
                        pvec_class_freq = vec_freq_cca_mo,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_cca,
                        pn_delta_mean = .1,
                        pn_gen_sd = l_gen_sd$CCa,
                        pb_verbose = TRUE))
```

```{r, include=FALSE}
n_mean_cca_an <- 5.62
n_sd_cca_an <- 1
vec_count_cca_an <- c(0,17,248,3463,8320,8874,5806)
vec_freq_cca_an <- vec_count_cca_an / sum(vec_count_cca_an)
```

```{r, include=FALSE}
(ev_cca_an <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cca_an,
                        pn_sd = n_sd_cca_an,
                        pvec_class_freq = vec_freq_cca_an,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_cca,
                        pn_delta_mean = .1,
                        pn_gen_sd = l_gen_sd$CCa,
                        pb_verbose = TRUE))
```

```{r, include=FALSE}
n_mean_cca_au <- 6.72
n_sd_cca_au <- 0.58
vec_count_cca_au <- c(0,0,1,20,125,485,2230)
vec_freq_cca_au <- vec_count_cca_au / sum(vec_count_cca_au)
```

```{r, include=FALSE}
(ev_cca_au <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cca_au,
                        pn_sd = n_sd_cca_au,
                        pvec_class_freq = vec_freq_cca_au,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_cca,
                        pn_delta_mean = .1,
                        pn_gen_sd = l_gen_sd$CCa,
                        pb_verbose = TRUE))
```

```{r, include=FALSE}
n_mean_cca_ch <- 6.65
n_sd_cca_ch <- 0.65
vec_count_cca_ch <- c(0,0,6,53,234,929,2210)
vec_freq_cca_ch <- vec_count_cca_ch / sum(vec_count_cca_ch)
```

```{r, include=FALSE}
(ev_cca_ch <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cca_ch,
                        pn_sd = n_sd_cca_ch,
                        pvec_class_freq = vec_freq_cca_ch,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_cca,
                        pn_delta_mean = .1,
                        pn_gen_sd = l_gen_sd$CCa,
                        pb_verbose = TRUE))
```

```{r, include=FALSE}
n_mean_cca_lm <- 6.56
n_sd_cca_lm <- 0.7
vec_count_cca_lm <- c(2,11,57,1041,6629,21068,56252)
vec_freq_cca_lm <- vec_count_cca_lm / sum(vec_count_cca_lm)
```


```{r, include=FALSE}
(ev_cca_lm <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cca_lm,
                        pn_sd = n_sd_cca_lm,
                        pvec_class_freq = vec_freq_cca_lm,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_cca,
                        pn_delta_mean = .1,
                        pn_gen_sd = l_gen_sd$CCa,
                        pb_verbose = TRUE))
```

##Carcass conformation calves (CCc)

```{r}
### # prices
vec_price_ccc <- c(11.2,12.7,13.6,14.2,14.7,15.2,15.7)
```

```{r, include=FALSE}
n_mean_ccc_ob <- 4.98
n_sd_ccc_ob <- 1.01
vec_count_ccc_ob <- c(11,94,451,2266,3486,2376,472)
vec_freq_ccc_ob <- vec_count_ccc_ob / sum(vec_count_ccc_ob)
```

```{r, include=FALSE}
(ev_ccc_ob <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_ccc_ob,
                        pn_sd = n_sd_ccc_ob,
                        pvec_class_freq = vec_freq_ccc_ob,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_ccc,
                        pn_delta_mean = .1,
                        pn_gen_sd = l_gen_sd$CCc,
                        pb_verbose = TRUE))
```

```{r, include=FALSE}
n_mean_ccc_bv <- 4.08
n_sd_ccc_bv <- 1.08
vec_count_ccc_bv <- c(1759,10739,42522,94581,40759,15082,4855)
vec_freq_ccc_bv <- vec_count_ccc_bv / sum(vec_count_ccc_bv)
```

```{r, include=FALSE}
(ev_ccc_bv <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_ccc_bv,
                        pn_sd = n_sd_ccc_bv,
                        pvec_class_freq = vec_freq_ccc_bv,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_ccc,
                        pn_delta_mean = .1,
                        pn_gen_sd = l_gen_sd$CCc,
                        pb_verbose = TRUE))
```

```{r, include=FALSE}
n_mean_ccc_si <- 5.33
n_sd_ccc_si <- 1.02
vec_count_ccc_si <- c(16,64,247,1620,3359,3374,1087)
vec_freq_ccc_si <- vec_count_ccc_si / sum(vec_count_ccc_si)
```


```{r, include=FALSE}
(ev_ccc_si <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_ccc_si,
                        pn_sd = n_sd_ccc_si,
                        pvec_class_freq = vec_freq_ccc_si,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_ccc,
                        pn_delta_mean = .1,
                        pn_gen_sd = l_gen_sd$CCc,
                        pb_verbose = TRUE))
```

```{r, include=FALSE}
n_mean_ccc_sf <- 3.88
n_sd_ccc_sf <- 1.08
vec_count_ccc_sf <- c(645,4027,13631,21453,9150,3054,626)
vec_freq_ccc_sf <- vec_count_ccc_sf / sum(vec_count_ccc_sf)
```


```{r, include=FALSE}
(ev_ccc_sf <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_ccc_sf,
                        pn_sd = n_sd_ccc_sf,
                        pvec_class_freq = vec_freq_ccc_sf,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_ccc,
                        pn_delta_mean = .1,
                        pn_gen_sd = l_gen_sd$CCc,
                        pb_verbose = TRUE))
```

```{r, include=FALSE}
n_mean_ccc_mo <- 4.73
n_sd_ccc_mo <- 1.11
vec_count_ccc_mo <- c(14,57,232,774,920,523,118)
vec_freq_ccc_mo <- vec_count_ccc_mo / sum(vec_count_ccc_mo)
```


```{r, include=FALSE}
(ev_ccc_mo <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_ccc_mo,
                        pn_sd = n_sd_ccc_mo,
                        pvec_class_freq = vec_freq_ccc_mo,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_ccc,
                        pn_delta_mean = .1,
                        pn_gen_sd = l_gen_sd$CCc,
                        pb_verbose = TRUE))
```

```{r, include=FALSE}
n_mean_ccc_an <- 5.48
n_sd_ccc_an <- 0.99
vec_count_ccc_an <- c(2,2,35,280,634,707,297)
vec_freq_ccc_an <- vec_count_ccc_an / sum(vec_count_ccc_an)
```


```{r, include=FALSE}
(ev_ccc_an <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_ccc_an,
                        pn_sd = n_sd_ccc_an,
                        pvec_class_freq = vec_freq_ccc_an,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_ccc,
                        pn_delta_mean = .1,
                        pn_gen_sd = l_gen_sd$CCc,
                        pb_verbose = TRUE))
```

```{r, include=FALSE}
n_mean_ccc_au <- 6.33
n_sd_ccc_au <- 1.04
vec_count_ccc_au <- c(0,1,0,3,6,14,36)
vec_freq_ccc_au <- vec_count_ccc_au / sum(vec_count_ccc_au)
```

```{r, include=FALSE}
(ev_ccc_au <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_ccc_au,
                        pn_sd = n_sd_ccc_au,
                        pvec_class_freq = vec_freq_ccc_au,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_ccc,
                        pn_delta_mean = .1,
                        pn_gen_sd = l_gen_sd$CCc,
                        pb_verbose = TRUE))
```

```{r, include=FALSE}
n_mean_ccc_ch <- 6.32
n_sd_ccc_ch <- 1.04
vec_count_ccc_ch <- c(0,0,1,3,5,9,31)
vec_freq_ccc_ch <- vec_count_ccc_ch / sum(vec_count_ccc_ch)
```


```{r, include=FALSE}
(ev_ccc_ch <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_ccc_ch,
                        pn_sd = n_sd_ccc_ch,
                        pvec_class_freq = vec_freq_ccc_ch,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_ccc,
                        pn_delta_mean = .1,
                        pn_gen_sd = l_gen_sd$CCc,
                        pb_verbose = TRUE))
```

```{r, include=FALSE}
n_mean_ccc_lm <- 6.55
n_sd_ccc_lm <- 0.77
vec_count_ccc_lm <- c(2,2,15,73,273,809,2472)
vec_freq_ccc_lm <- vec_count_ccc_lm / sum(vec_count_ccc_lm)
```

```{r, include=FALSE}
(ev_ccc_lm <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_ccc_lm,
                        pn_sd = n_sd_ccc_lm,
                        pvec_class_freq = vec_freq_ccc_lm,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_ccc,
                        pn_delta_mean = .1,
                        pn_gen_sd = l_gen_sd$CCc,
                        pb_verbose = TRUE))
```

##Carcass fatness adults (CFa)
```{r}
### # prices
vec_price_cfa <- c(-0.9000000,
-0.3000000,
0.0000000,
-0.3926929,
-0.8480817)
```

```{r, include=FALSE}
n_mean_cfa_ob <- 2.88
n_sd_cfa_ob <- 0.58
vec_count_cfa_ob <- c(161,889,4429,448,21)
vec_freq_cfa_ob <- vec_count_cfa_ob / sum(vec_count_cfa_ob)
```

```{r, include=FALSE}
(ev_cfa_ob<- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cfa_ob,
                        pn_sd = n_sd_cfa_ob,
                        pvec_class_freq = vec_freq_cfa_ob,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_cfa,
                        pn_delta_mean = .1,
                        pn_gen_sd = l_gen_sd$CFa,
                        pb_verbose = TRUE))
```

```{r, include=FALSE}
n_mean_cfa_bv <- 2.85
n_sd_cfa_bv <- 0.6
vec_count_cfa_bv <- c(1704,9941,41215,4167,214)
vec_freq_cfa_bv <- vec_count_cfa_bv / sum(vec_count_cfa_bv)
```

```{r, include=FALSE}
(ev_cfa_bv <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cfa_bv,
                        pn_sd = n_sd_cfa_bv,
                        pvec_class_freq = vec_freq_cfa_bv,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_cfa,
                        pn_delta_mean = .1,
                        pn_gen_sd = l_gen_sd$CFa,
                        pb_verbose = TRUE))
```

```{r, include=FALSE}
n_mean_cfa_si <- 2.82
n_sd_cfa_si <- 0.55
vec_count_cfa_si <- c(1259,10942,41326,3004,72)
vec_freq_cfa_si <- vec_count_cfa_si / sum(vec_count_cfa_si)
```

```{r, include=FALSE}
(ev_cfa_si <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cfa_si,
                        pn_sd = n_sd_cfa_si,
                        pvec_class_freq = vec_freq_cfa_si,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_cfa,
                        pn_delta_mean = .1,
                        pn_gen_sd = l_gen_sd$CFa,
                        pb_verbose = TRUE))
```

```{r, include=FALSE}
n_mean_cfa_sf <- 2.87
n_sd_cfa_sf <- 0.55
vec_count_cfa_sf <- c(787,5694,27214,2442,79)
vec_freq_cfa_sf <- vec_count_cfa_sf / sum(vec_count_cfa_sf)
```

```{r, include=FALSE}
(ev_cfa_sf <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cfa_sf,
                        pn_sd = n_sd_cfa_sf,
                        pvec_class_freq = vec_freq_cfa_sf,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_cfa,
                        pn_delta_mean = .1,
                        pn_gen_sd = l_gen_sd$CFa,
                        pb_verbose = TRUE))
```

```{r, include=FALSE}
n_mean_cfa_mo <- 2.68
n_sd_cfa_mo <- 0.6
vec_count_cfa_mo <- c(373,2721,6420,280,4)
vec_freq_cfa_mo <- vec_count_cfa_mo / sum(vec_count_cfa_mo)
```

```{r, include=FALSE}
(ev_cfa_mo <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cfa_mo,
                        pn_sd = n_sd_cfa_mo,
                        pvec_class_freq = vec_freq_cfa_mo,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_cfa,
                        pn_delta_mean = .1,
                        pn_gen_sd = l_gen_sd$CFa,
                        pb_verbose = TRUE))
```

```{r, include=FALSE}
n_mean_cfa_an <- 3.09
n_sd_cfa_an <- 0.74
vec_count_cfa_an <- c(803,3415,15694,6330,486)
vec_freq_cfa_an <- vec_count_cfa_an / sum(vec_count_cfa_an)
```

```{r, include=FALSE}
(ev_cfa_an <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cfa_an,
                        pn_sd = n_sd_cfa_an,
                        pvec_class_freq = vec_freq_cfa_an,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_cfa,
                        pn_delta_mean = .1,
                        pn_gen_sd = l_gen_sd$CFa,
                        pb_verbose = TRUE))
```

```{r, include=FALSE}
n_mean_cfa_au <- 2.65
n_sd_cfa_au <- 0.69
vec_count_cfa_au <- c(164,860,1664,169,4)
vec_freq_cfa_au <- vec_count_cfa_au / sum(vec_count_cfa_au)
```

```{r, include=FALSE}
(ev_cfa_au <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cfa_au,
                        pn_sd = n_sd_cfa_au,
                        pvec_class_freq = vec_freq_cfa_au,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_cfa,
                        pn_delta_mean = .1,
                        pn_gen_sd = l_gen_sd$CFa,
                        pb_verbose = TRUE))
```

```{r, include=FALSE}
n_mean_cfa_ch <- 2.63
n_sd_cfa_ch <- 0.71
vec_count_cfa_ch <- c(302,1354,2581,292,3)
vec_freq_cfa_ch <- vec_count_cfa_ch / sum(vec_count_cfa_ch)
```

```{r, include=FALSE}
(ev_cfa_ch <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cfa_ch,
                        pn_sd = n_sd_cfa_ch,
                        pvec_class_freq = vec_freq_cfa_ch,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_cfa,
                        pn_delta_mean = .1,
                        pn_gen_sd = l_gen_sd$CFa,
                        pb_verbose = TRUE))
```

```{r, include=FALSE}
n_mean_cfa_lm <- 2.71
n_sd_cfa_lm <- 0.71
vec_count_cfa_lm <- c(5106,21966,50669,7172,147)
vec_freq_cfa_lm <- vec_count_cfa_lm / sum(vec_count_cfa_lm)
```

```{r, include=FALSE}
(ev_cfa_lm <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cfa_lm,
                        pn_sd = n_sd_cfa_lm,
                        pvec_class_freq = vec_freq_cfa_lm,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_cfa,
                        pn_delta_mean = .1,
                        pn_gen_sd = l_gen_sd$CFa,
                        pb_verbose = TRUE))
```

##Carcass fatness calves (CFc)
```{r}
### # prices
vec_price_cfc <- c(-1.5,
-0.6,
0.0,
-0.4,
-1.0)
```

```{r, include=FALSE}
n_mean_cfc_ob <- 2.62
n_sd_cfc_ob <- 0.69
vec_count_cfc_ob <- c(632,2671,5379,471,3)
vec_freq_cfc_ob <- vec_count_cfc_ob / sum(vec_count_cfc_ob)
```

```{r, include=FALSE}
(ev_cfc_ob <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cfc_ob,
                        pn_sd = n_sd_cfc_ob,
                        pvec_class_freq = vec_freq_cfc_ob,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_cfc,
                        pn_delta_mean = .1,
                        pn_gen_sd = l_gen_sd$CFc,
                        pb_verbose = TRUE))
```

```{r, include=FALSE}
n_mean_cfc_bv <- 2.68
n_sd_cfc_bv <- 0.67
vec_count_cfc_bv <- c(12790,52626,133521,11316,44)
vec_freq_cfc_bv <- vec_count_cfc_bv / sum(vec_count_cfc_bv)
```

```{r, include=FALSE}
(ev_cfc_bv <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cfc_bv,
                        pn_sd = n_sd_cfc_bv,
                        pvec_class_freq = vec_freq_cfc_bv,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_cfc,
                        pn_delta_mean = .1,
                        pn_gen_sd = l_gen_sd$CFc,
                        pb_verbose = TRUE))
```

```{r, include=FALSE}
n_mean_cfc_si <- 2.66
n_sd_cfc_si <- 0.7
vec_count_cfc_si <- c(691,2522,5974,578,2)
vec_freq_cfc_si <- vec_count_cfc_si / sum(vec_count_cfc_si)
```

```{r, include=FALSE}
(ev_cfc_si <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cfc_si,
                        pn_sd = n_sd_cfc_si,
                        pvec_class_freq = vec_freq_cfc_si,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_cfc,
                        pn_delta_mean = .1,
                        pn_gen_sd = l_gen_sd$CFc,
                        pb_verbose = TRUE))
```

```{r, include=FALSE}
n_mean_cfc_sf <- 2.76
n_sd_cfc_sf <- 0.65
vec_count_cfc_sf <- c(2475,11464,35025,3602,19)
vec_freq_cfc_sf <- vec_count_cfc_sf / sum(vec_count_cfc_sf)
```

```{r, include=FALSE}
(ev_cfc_sf <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cfc_sf,
                        pn_sd = n_sd_cfc_sf,
                        pvec_class_freq = vec_freq_cfc_sf,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_cfc,
                        pn_delta_mean = .1,
                        pn_gen_sd = l_gen_sd$CFc,
                        pb_verbose = TRUE))
```

```{r, include=FALSE}
n_mean_cfc_mo <- 2.64
n_sd_cfc_mo <- 0.67
vec_count_cfc_mo <- c(191,676,1675,96,0)
vec_freq_cfc_mo <- vec_count_cfc_mo / sum(vec_count_cfc_mo)
```

```{r, include=FALSE}
(ev_cfc_mo <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cfc_mo,
                        pn_sd = n_sd_cfc_mo,
                        pvec_class_freq = vec_freq_cfc_mo,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_cfc,
                        pn_delta_mean = .1,
                        pn_gen_sd = l_gen_sd$CFc,
                        pb_verbose = TRUE))
```

```{r, include=FALSE}
n_mean_cfc_an <- 2.51
n_sd_cfc_an <- 0.76
vec_count_cfc_an <- c(187,706,936,126,2)
vec_freq_cfc_an <- vec_count_cfc_an / sum(vec_count_cfc_an)
```

```{r, include=FALSE}
(ev_cfc_an <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cfc_an,
                        pn_sd = n_sd_cfc_an,
                        pvec_class_freq = vec_freq_cfc_an,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_cfc,
                        pn_delta_mean = .1,
                        pn_gen_sd = l_gen_sd$CFc,
                        pb_verbose = TRUE))
```

```{r, include=FALSE}
n_mean_cfc_au <- 1.88
n_sd_cfc_au <- 0.78
vec_count_cfc_au <- c(22,23,15,0,0)
vec_freq_cfc_au <- vec_count_cfc_au / sum(vec_count_cfc_au)
```

```{r, include=FALSE}
(ev_cfc_au <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cfc_au,
                        pn_sd = n_sd_cfc_au,
                        pvec_class_freq = vec_freq_cfc_au,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_cfc,
                        pn_delta_mean = .1,
                        pn_gen_sd = l_gen_sd$CFc,
                        pb_verbose = TRUE))
```

```{r, include=FALSE}
n_mean_cfc_ch <- 2.06
n_sd_cfc_ch <- 0.91
vec_count_cfc_ch <- c(18,12,19,1,0)
vec_freq_cfc_ch <- vec_count_cfc_ch / sum(vec_count_cfc_ch)
```

```{r, include=FALSE}
(ev_cfc_ch <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cfc_ch,
                        pn_sd = n_sd_cfc_ch,
                        pvec_class_freq = vec_freq_cfc_ch,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_cfc,
                        pn_delta_mean = .1,
                        pn_gen_sd = l_gen_sd$CFc,
                        pb_verbose = TRUE))
```

```{r, include=FALSE}
n_mean_cfc_lm <- 2.21
n_sd_cfc_lm <- 0.77
vec_count_cfc_lm <- c(730,1495,1358,63,0)
vec_freq_cfc_lm <- vec_count_cfc_lm / sum(vec_count_cfc_lm)
```

```{r, include=FALSE}
(ev_cfc_lm <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cfc_lm,
                        pn_sd = n_sd_cfc_lm,
                        pvec_class_freq = vec_freq_cfc_lm,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_cfc,
                        pn_delta_mean = .1,
                        pn_gen_sd = l_gen_sd$CFc,
                        pb_verbose = TRUE))
```

##Carcass weight adults (CWa)

```{r}
 n_scale_fact_cwa <- 100
vec_price_cwa <- c(0.0,
-0.1,
-0.2,
-0.3,
-0.5,
-0.7,
-0.9,
-1.2,
-1.4,
-1.6,
-1.8)
vec_thre_cwa <- c(2.9,
3.0,
3.1,
3.2,
3.3,
3.4,
3.5,
3.6,
3.7,
3.8) * n_scale_fact_cwa
```

```{r, include=FALSE}
n_mean_cwa_ob <- 2.61 * n_scale_fact_cwa
n_sd_cwa_ob <- 0.41 * n_scale_fact_cwa
```

```{r, include=FALSE}
(ev_cwa_ob <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cwa_ob,
                        pn_sd = n_sd_cwa_ob,
                        pvec_class_freq = NULL,
                        pvec_threshold = vec_thre_cwa,
                        pvec_price = vec_price_cwa,
                        pn_gen_sd = l_gen_sd$CWa * n_scale_fact_cwa,
                        pn_delta_mean = .01 * n_scale_fact_cwa))

```

```{r, include=FALSE}
n_mean_cwa_bv <- 2.77 * n_scale_fact_cwa
n_sd_cwa_bv <- 0.36 * n_scale_fact_cwa
```

```{r, include=FALSE}
(ev_cwa_bv <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cwa_bv,
                        pn_sd = n_sd_cwa_bv,
                        pvec_class_freq = NULL,
                        pvec_threshold = vec_thre_cwa,
                        pvec_price = vec_price_cwa,
                        pn_gen_sd = l_gen_sd$CWa * n_scale_fact_cwa,
                        pn_delta_mean = .01 * n_scale_fact_cwa))

```

```{r, include=FALSE}
n_mean_cwa_si <- 2.79 * n_scale_fact_cwa
n_sd_cwa_si <- 0.42 * n_scale_fact_cwa
```

```{r, include=FALSE}
(ev_cwa_si <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cwa_si,
                        pn_sd = n_sd_cwa_si,
                        pvec_class_freq = NULL,
                        pvec_threshold = vec_thre_cwa,
                        pvec_price = vec_price_cwa,
                        pn_gen_sd = l_gen_sd$CWa * n_scale_fact_cwa,
                        pn_delta_mean = .01 * n_scale_fact_cwa))

```

```{r, include=FALSE}
n_mean_cwa_sf <- 2.88 * n_scale_fact_cwa
n_sd_cwa_sf <- 0.32 * n_scale_fact_cwa
```

```{r, include=FALSE}
(ev_cwa_sf <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cwa_sf,
                        pn_sd = n_sd_cwa_sf,
                        pvec_class_freq = NULL,
                        pvec_threshold = vec_thre_cwa,
                        pvec_price = vec_price_cwa,
                        pn_gen_sd = l_gen_sd$CWa * n_scale_fact_cwa,
                        pn_delta_mean = .01 * n_scale_fact_cwa))

```

```{r, include=FALSE}
n_mean_cwa_mo <- 2.99 * n_scale_fact_cwa
n_sd_cwa_mo <- 0.25 * n_scale_fact_cwa
```

```{r, include=FALSE}
(ev_cwa_mo <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cwa_mo,
                        pn_sd = n_sd_cwa_mo,
                        pvec_class_freq = NULL,
                        pvec_threshold = vec_thre_cwa,
                        pvec_price = vec_price_cwa,
                        pn_gen_sd = l_gen_sd$CWa * n_scale_fact_cwa,
                        pn_delta_mean = .01 * n_scale_fact_cwa))

```

```{r, include=FALSE}
n_mean_cwa_an <- 2.32 * n_scale_fact_cwa
n_sd_cwa_an <- 0.53 * n_scale_fact_cwa
```

```{r, include=FALSE}
(ev_cwa_an <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cwa_an,
                        pn_sd = n_sd_cwa_an,
                        pvec_class_freq = NULL,
                        pvec_threshold = vec_thre_cwa,
                        pvec_price = vec_price_cwa,
                        pn_gen_sd = l_gen_sd$CWa * n_scale_fact_cwa,
                        pn_delta_mean = .01 * n_scale_fact_cwa))

```

```{r, include=FALSE}
n_mean_cwa_au <- 2.77 * n_scale_fact_cwa
n_sd_cwa_au <- 0.54 * n_scale_fact_cwa
```

```{r, include=FALSE}
(ev_cwa_au <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cwa_au,
                        pn_sd = n_sd_cwa_au,
                        pvec_class_freq = NULL,
                        pvec_threshold = vec_thre_cwa,
                        pvec_price = vec_price_cwa,
                        pn_gen_sd = l_gen_sd$CWa * n_scale_fact_cwa,
                        pn_delta_mean = .01 * n_scale_fact_cwa))

```

```{r, include=FALSE}
n_mean_cwa_ch <- 2.91 * n_scale_fact_cwa
n_sd_cwa_ch <- 0.55 * n_scale_fact_cwa
```

```{r, include=FALSE}
(ev_cwa_ch <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cwa_ch,
                        pn_sd = n_sd_cwa_ch,
                        pvec_class_freq = NULL,
                        pvec_threshold = vec_thre_cwa,
                        pvec_price = vec_price_cwa,
                        pn_gen_sd = l_gen_sd$CWa * n_scale_fact_cwa,
                        pn_delta_mean = .01 * n_scale_fact_cwa))

```

```{r, include=FALSE}
n_mean_cwa_lm <- 2.42 * n_scale_fact_cwa
n_sd_cwa_lm <- 0.45 * n_scale_fact_cwa
```

```{r, include=FALSE}
(ev_cwa_lm <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cwa_lm,
                        pn_sd = n_sd_cwa_lm,
                        pvec_class_freq = NULL,
                        pvec_threshold = vec_thre_cwa,
                        pvec_price = vec_price_cwa,
                        pn_gen_sd = l_gen_sd$CWa * n_scale_fact_cwa,
                        pn_delta_mean = .01 * n_scale_fact_cwa))

```

##Carcass weight calves (CWc)
```{r}
n_scale_fact_cwc <- 100
vec_price_cwc <- seq(0.0,-1.1,-0.1);vec_price_cwc
vec_thre_cwc <- seq(1.4, 1.5, 0.01) * n_scale_fact_cwc
vec_thre_cwc
```

```{r, include=FALSE}
n_mean_cwc_ob <- 1.25 * n_scale_fact_cwc
n_sd_cwc_ob <- 0.13 * n_scale_fact_cwc
```

```{r, include=FALSE}
(ev_cwc_ob <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cwc_ob,
                        pn_sd = n_sd_cwc_ob,
                        pvec_class_freq = NULL,
                        pvec_threshold = vec_thre_cwc,
                        pvec_price = vec_price_cwc,
                        pn_gen_sd = l_gen_sd$CWc * n_scale_fact_cwc,
                        pn_delta_mean = .01 * n_scale_fact_cwc))

```

```{r, include=FALSE}
n_mean_cwc_bv <- 1.26 * n_scale_fact_cwc
n_sd_cwc_bv <- 0.14 * n_scale_fact_cwc
```

```{r, include=FALSE}
(ev_cwc_bv <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cwc_bv,
                        pn_sd = n_sd_cwc_bv,
                        pvec_class_freq = NULL,
                        pvec_threshold = vec_thre_cwc,
                        pvec_price = vec_price_cwc,
                        pn_gen_sd = l_gen_sd$CWc * n_scale_fact_cwc,
                        pn_delta_mean = .01 * n_scale_fact_cwc))

```

```{r, include=FALSE}
n_mean_cwc_si <- 1.27 * n_scale_fact_cwc
n_sd_cwc_si <- 0.13 * n_scale_fact_cwc
```

```{r, include=FALSE}
(ev_cwc_si <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cwc_si,
                        pn_sd = n_sd_cwc_si,
                        pvec_class_freq = NULL,
                        pvec_threshold = vec_thre_cwc,
                        pvec_price = vec_price_cwc,
                        pn_gen_sd = l_gen_sd$CWc * n_scale_fact_cwc,
                        pn_delta_mean = .01 * n_scale_fact_cwc))

```

```{r, include=FALSE}
n_mean_cwc_sf <- 1.24 * n_scale_fact_cwc
n_sd_cwc_sf <- 0.13 * n_scale_fact_cwc
```

```{r, include=FALSE}
(ev_cwc_sf <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cwc_sf,
                        pn_sd = n_sd_cwc_sf,
                        pvec_class_freq = NULL,
                        pvec_threshold = vec_thre_cwc,
                        pvec_price = vec_price_cwc,
                        pn_gen_sd = l_gen_sd$CWc * n_scale_fact_cwc,
                        pn_delta_mean = .01 * n_scale_fact_cwc))

```

```{r, include=FALSE}
n_mean_cwc_mo <- 1.28 * n_scale_fact_cwc
n_sd_cwc_mo <- 0.15 * n_scale_fact_cwc
```

```{r, include=FALSE}
(ev_cwc_mo <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cwc_mo,
                        pn_sd = n_sd_cwc_mo,
                        pvec_class_freq = NULL,
                        pvec_threshold = vec_thre_cwc,
                        pvec_price = vec_price_cwc,
                        pn_gen_sd = l_gen_sd$CWc * n_scale_fact_cwc,
                        pn_delta_mean = .01 * n_scale_fact_cwc))

```

```{r, include=FALSE}
n_mean_cwc_an <- 1.23 * n_scale_fact_cwa
n_sd_cwc_an <- 0.14 * n_scale_fact_cwa
```

```{r, include=FALSE}
(ev_cwc_an <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cwc_an,
                        pn_sd = n_sd_cwc_an,
                        pvec_class_freq = NULL,
                        pvec_threshold = vec_thre_cwc,
                        pvec_price = vec_price_cwc,
                        pn_gen_sd = l_gen_sd$CWc * n_scale_fact_cwc,
                        pn_delta_mean = .01 * n_scale_fact_cwc))

```

```{r, include=FALSE}
n_mean_cwc_au <- 1.25 * n_scale_fact_cwa
n_sd_cwc_au <- 0.18 * n_scale_fact_cwa
```

```{r, include=FALSE}
(ev_cwc_au <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cwc_au,
                        pn_sd = n_sd_cwc_au,
                        pvec_class_freq = NULL,
                        pvec_threshold = vec_thre_cwc,
                        pvec_price = vec_price_cwc,
                        pn_gen_sd = l_gen_sd$CWc * n_scale_fact_cwc,
                        pn_delta_mean = .01 * n_scale_fact_cwc))

```

```{r, include=FALSE}
n_mean_cwc_ch <- 1.27 * n_scale_fact_cwa
n_sd_cwc_ch <- 0.15 * n_scale_fact_cwa
```

```{r, include=FALSE}
(ev_cwc_ch <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cwc_ch,
                        pn_sd = n_sd_cwc_ch,
                        pvec_class_freq = NULL,
                        pvec_threshold = vec_thre_cwc,
                        pvec_price = vec_price_cwc,
                        pn_gen_sd = l_gen_sd$CWc * n_scale_fact_cwc,
                        pn_delta_mean = .01 * n_scale_fact_cwc))

```

```{r, include=FALSE}
n_mean_cwc_lm <- 1.31 * n_scale_fact_cwa
n_sd_cwc_lm <- 0.12 * n_scale_fact_cwa
```

```{r, include=FALSE}
(ev_cwc_lm <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cwc_lm,
                        pn_sd = n_sd_cwc_lm,
                        pvec_class_freq = NULL,
                        pvec_threshold = vec_thre_cwc,
                        pvec_price = vec_price_cwc,
                        pn_gen_sd = l_gen_sd$CWc * n_scale_fact_cwc,
                        pn_delta_mean = .01 * n_scale_fact_cwc))

```

## Overview of the phenotypic mean
```{r, eval=TRUE, echo=FALSE, results="asis"}
tbl_population_mean <- tibble::data_frame(Traits = c("cca", "ccc", "cfa", "cfc", "cwa", "cwc"),
                                    OB = c(n_mean_cca_ob,
                                           n_mean_ccc_ob,
                                           n_mean_cfa_ob,
                                           n_mean_cfc_ob,
                                           n_mean_cwa_ob,
                                           n_mean_cwc_ob),
                                    BV = c(n_mean_cca_bv,
                                           n_mean_ccc_bv,
                                           n_mean_cfa_bv,
                                           n_mean_cfc_bv,
                                           n_mean_cwa_bv,
                                           n_mean_cwc_bv),
                                    SI = c(n_mean_cca_si,
                                           n_mean_ccc_si,
                                           n_mean_cfa_si,
                                           n_mean_cfc_si,
                                           n_mean_cwa_si,
                                           n_mean_cwc_si),
                                    SF = c(n_mean_cca_sf,
                                           n_mean_ccc_sf,
                                           n_mean_cfa_sf,
                                           n_mean_cfc_sf,
                                           n_mean_cwa_sf,
                                           n_mean_cwc_sf),
                                    MO = c(n_mean_cca_mo,
                                           n_mean_ccc_mo,
                                           n_mean_cfa_mo,
                                           n_mean_cfc_mo,
                                           n_mean_cwa_mo,
                                           n_mean_cwc_mo),
                                    AN = c(n_mean_cca_an,
                                           n_mean_ccc_an,
                                           n_mean_cfa_an,
                                           n_mean_cfc_an,
                                           n_mean_cwa_an,
                                           n_mean_cwc_an),
                                    AU = c(n_mean_cca_au,
                                           n_mean_ccc_au,
                                           n_mean_cfa_au,
                                           n_mean_cfc_au,
                                           n_mean_cwa_au,
                                           n_mean_cwc_au),
                                    CH = c(n_mean_cca_ch,
                                           n_mean_ccc_ch,
                                           n_mean_cfa_ch,
                                           n_mean_cfc_ch,
                                           n_mean_cwa_ch,
                                           n_mean_cwc_ch),
                                    LM = c(n_mean_cca_lm,
                                           n_mean_ccc_lm,
                                           n_mean_cfa_lm,
                                           n_mean_cfc_lm,
                                           n_mean_cwa_lm,
                                           n_mean_cwc_lm))


knitr::kable(tbl_population_mean,booktabs = TRUE)
```

## Presenting output for economic values
The computed economic values are shown in the following tables:

###1.1) Table are presenting economic value in trait unit.
```{r, eval=TRUE, echo=FALSE, results="asis"}
tbl_ev_result_ev_per_trait_unit <- tibble::data_frame(Traits = c("cca", "ccc", "cfa", "cfc", "cwa", "cwc"),
                                    OB = c(ev_cca_ob$ev_per_trait_unit, 
                                            ev_ccc_ob$ev_per_trait_unit, 
                                            ev_cfa_ob$ev_per_trait_unit, 
                                            ev_cfc_ob$ev_per_trait_unit, 
                                            ev_cwa_ob$ev_per_trait_unit, 
                                            ev_cwc_ob$ev_per_trait_unit),
                                    BV = c(ev_cca_bv$ev_per_trait_unit, 
                                            ev_ccc_bv$ev_per_trait_unit, 
                                            ev_cfa_bv$ev_per_trait_unit, 
                                            ev_cfc_bv$ev_per_trait_unit, 
                                            ev_cwa_bv$ev_per_trait_unit, 
                                            ev_cwc_bv$ev_per_trait_unit),
                                    SI = c(ev_cca_si$ev_per_trait_unit, 
                                            ev_ccc_si$ev_per_trait_unit, 
                                            ev_cfa_si$ev_per_trait_unit, 
                                            ev_cfc_si$ev_per_trait_unit, 
                                            ev_cwa_si$ev_per_trait_unit, 
                                            ev_cwc_si$ev_per_trait_unit),
                                    SF = c(ev_cca_sf$ev_per_trait_unit, 
                                            ev_ccc_sf$ev_per_trait_unit, 
                                            ev_cfa_sf$ev_per_trait_unit, 
                                            ev_cfc_sf$ev_per_trait_unit, 
                                            ev_cwa_sf$ev_per_trait_unit, 
                                            ev_cwc_sf$ev_per_trait_unit),
                                    MO = c(ev_cca_mo$ev_per_trait_unit, 
                                            ev_ccc_mo$ev_per_trait_unit, 
                                            ev_cfa_mo$ev_per_trait_unit, 
                                            ev_cfc_mo$ev_per_trait_unit, 
                                            ev_cwa_mo$ev_per_trait_unit, 
                                            ev_cwc_mo$ev_per_trait_unit),
                                    AN = c(ev_cca_an$ev_per_trait_unit, 
                                            ev_ccc_an$ev_per_trait_unit, 
                                            ev_cfa_an$ev_per_trait_unit, 
                                            ev_cfc_an$ev_per_trait_unit, 
                                            ev_cwa_an$ev_per_trait_unit, 
                                            ev_cwc_an$ev_per_trait_unit),
                                    AU = c(ev_cca_au$ev_per_trait_unit, 
                                            ev_ccc_au$ev_per_trait_unit, 
                                            ev_cfa_au$ev_per_trait_unit, 
                                            ev_cfc_au$ev_per_trait_unit, 
                                            ev_cwa_au$ev_per_trait_unit, 
                                            ev_cwc_au$ev_per_trait_unit),
                                    CH = c(ev_cca_ch$ev_per_trait_unit, 
                                            ev_ccc_ch$ev_per_trait_unit, 
                                            ev_cfa_ch$ev_per_trait_unit, 
                                            ev_cfc_ch$ev_per_trait_unit, 
                                            ev_cwa_ch$ev_per_trait_unit, 
                                            ev_cwc_ch$ev_per_trait_unit),
                                    LM = c(ev_cca_lm$ev_per_trait_unit, 
                                            ev_ccc_lm$ev_per_trait_unit, 
                                            ev_cfa_lm$ev_per_trait_unit, 
                                            ev_cfc_lm$ev_per_trait_unit, 
                                            ev_cwa_lm$ev_per_trait_unit, 
                                            ev_cwc_lm$ev_per_trait_unit))


knitr::kable(tbl_ev_result_ev_per_trait_unit,booktabs = TRUE)
```

###1.2) Table are presenting economic value in genetic standard deviation.
```{r, eval=TRUE, echo=FALSE, results="asis"}
tbl_ev_result_ev_per_gen_sd <- tibble::data_frame(Traits = c("cca", "ccc", "cfa", "cfc", "cwa", "cwc"),
                                    OB = c(ev_cca_ob$ev_per_gen_sd,
                                            ev_ccc_ob$ev_per_gen_sd, 
                                            ev_cfa_ob$ev_per_gen_sd, 
                                            ev_cfc_ob$ev_per_gen_sd, 
                                            ev_cwa_ob$ev_per_gen_sd, 
                                            ev_cwc_ob$ev_per_gen_sd),
                                    BV = c(ev_cca_bv$ev_per_gen_sd, 
                                            ev_ccc_bv$ev_per_gen_sd, 
                                            ev_cfa_bv$ev_per_gen_sd, 
                                            ev_cfc_bv$ev_per_gen_sd, 
                                            ev_cwa_bv$ev_per_gen_sd, 
                                            ev_cwc_bv$ev_per_gen_sd),
                                    SI = c(ev_cca_si$ev_per_gen_sd, 
                                            ev_ccc_si$ev_per_gen_sd, 
                                            ev_cfa_si$ev_per_gen_sd, 
                                            ev_cfc_si$ev_per_gen_sd, 
                                            ev_cwa_si$ev_per_gen_sd, 
                                            ev_cwc_si$ev_per_gen_sd),
                                    SF = c(ev_cca_sf$ev_per_gen_sd, 
                                            ev_ccc_sf$ev_per_gen_sd, 
                                            ev_cfa_sf$ev_per_gen_sd, 
                                            ev_cfc_sf$ev_per_gen_sd, 
                                            ev_cwa_sf$ev_per_gen_sd, 
                                            ev_cwc_sf$ev_per_gen_sd),
                                    MO = c(ev_cca_mo$ev_per_gen_sd, 
                                            ev_ccc_mo$ev_per_gen_sd, 
                                            ev_cfa_mo$ev_per_gen_sd, 
                                            ev_cfc_mo$ev_per_gen_sd, 
                                            ev_cwa_mo$ev_per_gen_sd, 
                                            ev_cwc_mo$ev_per_gen_sd),
                                    AN = c(ev_cca_an$ev_per_gen_sd,
                                            ev_ccc_an$ev_per_gen_sd, 
                                            ev_cfa_an$ev_per_gen_sd, 
                                            ev_cfc_an$ev_per_gen_sd, 
                                            ev_cwa_an$ev_per_gen_sd, 
                                            ev_cwc_an$ev_per_gen_sd),
                                    AU = c(ev_cca_au$ev_per_gen_sd, 
                                            ev_ccc_au$ev_per_gen_sd, 
                                            ev_cfa_au$ev_per_gen_sd, 
                                            ev_cfc_au$ev_per_gen_sd, 
                                            ev_cwa_au$ev_per_gen_sd, 
                                            ev_cwc_au$ev_per_gen_sd),
                                    CH = c(ev_cca_ch$ev_per_gen_sd, 
                                            ev_ccc_ch$ev_per_gen_sd, 
                                            ev_cfa_ch$ev_per_gen_sd, 
                                            ev_cfc_ch$ev_per_gen_sd, 
                                            ev_cwa_ch$ev_per_gen_sd, 
                                            ev_cwc_ch$ev_per_gen_sd),
                                    LM = c(ev_cca_lm$ev_per_gen_sd, 
                                            ev_ccc_lm$ev_per_gen_sd, 
                                            ev_cfa_lm$ev_per_gen_sd, 
                                            ev_cfc_lm$ev_per_gen_sd, 
                                            ev_cwa_lm$ev_per_gen_sd, 
                                            ev_cwc_lm$ev_per_gen_sd))


knitr::kable(tbl_ev_result_ev_per_gen_sd,booktabs = TRUE)
```

##2. Computing Relative Economic Factors
Relative economic factors are defined as the ratio of each economic value on the basis of one genetic standard deviation to the sum of all economic values in a given breed.

```{r, echo=FALSE}
### # compute factors with function
tbl_rel_factors <- MeatValueIndex::get_relative_economic_factors(ptbl_economic_value = tbl_ev_result_ev_per_gen_sd,
                                                 pb_first_col_trait_name = TRUE)
knitr::kable(tbl_rel_factors, booktabs = TRUE)
```

##3. Importance of calves versus adults for each population
```{r, include=FALSE}
tbl_number_calves_adults <- tibble::data_frame(Categories = c("adults", "calves"),
                                    OB = c(5948,
                                           9156),
                                    BV = c(57241, 
                                          210297),
                                    SI = c(56603, 
                                           9767),
                                    SF = c(36216, 
                                           52585),
                                    MO = c(9798, 
                                           2638),
                                    AN = c(26728,
                                           1957),
                                    AU = c(2861, 
                                          60),
                                    CH = c(4532, 
                                           50),
                                    LM = c(85060, 
                                           3646))


knitr::kable(tbl_number_calves_adults,booktabs = TRUE)
```

```{r, include=FALSE}
### # Proportion of the slaughtercategories for each breed
tbl_proportion <- MeatValueIndex::get_relative_economic_factors(ptbl_economic_value = tbl_number_calves_adults,
                                                                      pb_first_col_trait_name = TRUE)
```

```{r, echo=FALSE}
knitr::kable(tbl_proportion, booktabs = TRUE)
```

##4. Szenarios
### Szenario A) we are using the relative economic factors (table 2)
### Szenario B) The relative factors are weighted with animal categories to get weighted relative factors (File name: weighted_economic_value_relative_allBreeds.csv)
```{r, include=FALSE}
(tbl_proportion4eachtrait <- bind_rows(tbl_proportion,tbl_proportion,tbl_proportion))
(tbl_proportion4eachtrait <- tbl_proportion4eachtrait[, 2:ncol(tbl_proportion4eachtrait)])
(tbl_proportion4eachtrait <- bind_cols(tbl_rel_factors[,1], tbl_proportion4eachtrait))
(colnames(tbl_proportion4eachtrait) <- colnames(tbl_rel_factors))

tbl_weighted_rel_factors <- MeatValueIndex::weight_economic_value(ptbl_economic_value = tbl_rel_factors,
                                     ptbl_weight = tbl_proportion4eachtrait,
                                     pb_first_col_trait_name = TRUE)
```

```{r, echo=FALSE}
knitr::kable(tbl_weighted_rel_factors,booktabs = TRUE)
```


```{r, include=FALSE}
MeatValueIndex::write_ev_to_file(ptbl_economic_value = tbl_weighted_rel_factors,
                                ps_out_path = "weighted_economic_value_relative_allBreeds.csv",
                                pb_first_col_trait_name = TRUE)
```
