---
title: "DualBreed"
author: "Sophie Kunz and Peter von Rohr"
date: "2 November 2018"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(dplyr)
```


#1. Computing Economic Value For Dual Breed

## Genetic Standard Deviations
Economic values can also be given in terms of a change of one genetic standard deviation. The used estimates for this parameter are

```{r}
l_gen_sd <- list(CCc = 0.6336,
                 CCa = 0.6335,
                 CFc = 0.3474,
                 CFa = 0.3609,
                 CWc = 0.0557,
                 CWa = 0.1395)
```


##Carcass conformation adults (CCa)
```{r}
### # prices
vec_price_cca <- c(7.526960,7.938872,8.450784,8.800000,9.137304,9.392693,9.642693)
```


###OB
```{r}
n_mean_cca_ob <- 5.20
n_sd_cca_ob <- 1.02
vec_count_cca_ob <- c(4,43,218,1150,2106,1905,522)
vec_freq_cca_ob <- vec_count_cca_ob / sum(vec_count_cca_ob)
```

```{r, include=FALSE}
(ev_cca_ob <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cca_ob,
                        pn_sd = n_sd_cca_ob,
                        pvec_class_freq = vec_freq_cca_ob,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_cca,
                        pn_delta_mean = .1,
                        pn_gen_sd = l_gen_sd$CCa,
                        pb_verbose = TRUE))
```

###BV
```{r}
n_mean_cca_bv <- 4.78
n_sd_cca_bv <- 1.27
vec_count_cca_bv <- c(273,1562,5982,17808,14303,11438,5875)
vec_freq_cca_bv <- vec_count_cca_bv / sum(vec_count_cca_bv)

```

```{r, include=FALSE}
(ev_cca_bv <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cca_bv,
                        pn_sd = n_sd_cca_bv,
                        pvec_class_freq = vec_freq_cca_bv,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_cca,
                        pn_delta_mean = .1,
                        pn_gen_sd = l_gen_sd$CCa,
                        pb_verbose = TRUE))
```

###SI
```{r}
n_mean_cca_si <- 5.83
n_sd_cca_si <- 0.9
vec_count_cca_si <- c(4,38,377,3994,13917,24738,13535)
vec_freq_cca_si <- vec_count_cca_si / sum(vec_count_cca_si)
```

```{r, include=FALSE}
(ev_cca_si <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cca_si,
                        pn_sd = n_sd_cca_si,
                        pvec_class_freq = vec_freq_cca_si,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_cca,
                        pn_delta_mean = .1,
                        pn_gen_sd = l_gen_sd$CCa,
                        pb_verbose = TRUE))
```

###SF
```{r}
n_mean_cca_sf <- 4.57
n_sd_cca_sf <- 1.18
vec_count_cca_sf <- c(165,1189,4814,11545,10445,6303,1755)
vec_freq_cca_sf <- vec_count_cca_sf / sum(vec_count_cca_sf)
```

```{r, include=FALSE}
(ev_cca_sf <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cca_sf,
                        pn_sd = n_sd_cca_sf,
                        pvec_class_freq = vec_freq_cca_sf,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_cca,
                        pn_delta_mean = .1,
                        pn_gen_sd = l_gen_sd$CCa,
                        pb_verbose = TRUE))
```

###MO
```{r}
n_mean_cca_mo <- 5.39
n_sd_cca_mo <- 0.94
vec_count_cca_mo <- c(10,33,194,1341,3511,3730,979)
vec_freq_cca_mo <- vec_count_cca_mo / sum(vec_count_cca_mo)
```

```{r, include=FALSE}
(ev_cca_mo <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cca_mo,
                        pn_sd = n_sd_cca_mo,
                        pvec_class_freq = vec_freq_cca_mo,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_cca,
                        pn_delta_mean = .1,
                        pn_gen_sd = l_gen_sd$CCa,
                        pb_verbose = TRUE))
```

##Carcass conformation calves (CCc)

```{r}
### # prices
vec_price_ccc <- c(11.2,12.7,13.6,14.2,14.7,15.2,15.7)
```

###OB
```{r}
n_mean_ccc_ob <- 4.98
n_sd_ccc_ob <- 1.01
vec_count_ccc_ob <- c(11,94,451,2266,3486,2376,472)
vec_freq_ccc_ob <- vec_count_ccc_ob / sum(vec_count_ccc_ob)
```

```{r, include=FALSE}
(ev_ccc_ob <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_ccc_ob,
                        pn_sd = n_sd_ccc_ob,
                        pvec_class_freq = vec_freq_ccc_ob,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_ccc,
                        pn_delta_mean = .1,
                        pn_gen_sd = l_gen_sd$CCc,
                        pb_verbose = TRUE))
```

###BV
```{r}
n_mean_ccc_bv <- 4.08
n_sd_ccc_bv <- 1.08
vec_count_ccc_bv <- c(1759,10739,42522,94581,40759,15082,4855)
vec_freq_ccc_bv <- vec_count_ccc_bv / sum(vec_count_ccc_bv)
```

```{r, include=FALSE}
(ev_ccc_bv <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_ccc_bv,
                        pn_sd = n_sd_ccc_bv,
                        pvec_class_freq = vec_freq_ccc_bv,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_ccc,
                        pn_delta_mean = .1,
                        pn_gen_sd = l_gen_sd$CCc,
                        pb_verbose = TRUE))
```

###SI
```{r}
n_mean_ccc_si <- 5.33
n_sd_ccc_si <- 1.02
vec_count_ccc_si <- c(16,64,247,1620,3359,3374,1087)
vec_freq_ccc_si <- vec_count_ccc_si / sum(vec_count_ccc_si)
```


```{r, include=FALSE}
(ev_ccc_si <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_ccc_si,
                        pn_sd = n_sd_ccc_si,
                        pvec_class_freq = vec_freq_ccc_si,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_ccc,
                        pn_delta_mean = .1,
                        pn_gen_sd = l_gen_sd$CCc,
                        pb_verbose = TRUE))
```

###SF
```{r}
n_mean_ccc_sf <- 3.88
n_sd_ccc_sf <- 1.08
vec_count_ccc_sf <- c(645,4027,13631,21453,9150,3054,626)
vec_freq_ccc_sf <- vec_count_ccc_sf / sum(vec_count_ccc_sf)
```


```{r, include=FALSE}
(ev_ccc_sf <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_ccc_sf,
                        pn_sd = n_sd_ccc_sf,
                        pvec_class_freq = vec_freq_ccc_sf,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_ccc,
                        pn_delta_mean = .1,
                        pn_gen_sd = l_gen_sd$CCc,
                        pb_verbose = TRUE))
```

###MO
```{r}
n_mean_ccc_mo <- 4.73
n_sd_ccc_mo <- 1.11
vec_count_ccc_mo <- c(14,57,232,774,920,523,118)
vec_freq_ccc_mo <- vec_count_ccc_mo / sum(vec_count_ccc_mo)
```


```{r, include=FALSE}
(ev_ccc_mo <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_ccc_mo,
                        pn_sd = n_sd_ccc_mo,
                        pvec_class_freq = vec_freq_ccc_mo,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_ccc,
                        pn_delta_mean = .1,
                        pn_gen_sd = l_gen_sd$CCc,
                        pb_verbose = TRUE))
```



##Carcass fatness adults (CFa)
```{r}
### # prices
vec_price_cfa <- c(-0.9000000,
-0.3000000,
0.0000000,
-0.3926929,
-0.8480817)
```

###OB
```{r}
n_mean_cfa_ob <- 2.88
n_sd_cfa_ob <- 0.58
vec_count_cfa_ob <- c(161,889,4429,448,21)
vec_freq_cfa_ob <- vec_count_cfa_ob / sum(vec_count_cfa_ob)
```


```{r, include=FALSE}
(ev_cfa_ob<- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cfa_ob,
                        pn_sd = n_sd_cfa_ob,
                        pvec_class_freq = vec_freq_cfa_ob,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_cfa,
                        pn_delta_mean = .1,
                        pn_gen_sd = l_gen_sd$CFa,
                        pb_verbose = TRUE))
```

###BV
```{r}
n_mean_cfa_bv <- 2.85
n_sd_cfa_bv <- 0.6
vec_count_cfa_bv <- c(1704,9941,41215,4167,214)
vec_freq_cfa_bv <- vec_count_cfa_bv / sum(vec_count_cfa_bv)
```


```{r, include=FALSE}
(ev_cfa_bv <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cfa_bv,
                        pn_sd = n_sd_cfa_bv,
                        pvec_class_freq = vec_freq_cfa_bv,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_cfa,
                        pn_delta_mean = .1,
                        pn_gen_sd = l_gen_sd$CFa,
                        pb_verbose = TRUE))
```

###SI
```{r}
n_mean_cfa_si <- 2.82
n_sd_cfa_si <- 0.55
vec_count_cfa_si <- c(1259,10942,41326,3004,72)
vec_freq_cfa_si <- vec_count_cfa_si / sum(vec_count_cfa_si)
```


```{r, include=FALSE}
(ev_cfa_si <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cfa_si,
                        pn_sd = n_sd_cfa_si,
                        pvec_class_freq = vec_freq_cfa_si,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_cfa,
                        pn_delta_mean = .1,
                        pn_gen_sd = l_gen_sd$CFa,
                        pb_verbose = TRUE))
```

###SF
```{r}
n_mean_cfa_sf <- 2.87
n_sd_cfa_sf <- 0.55
vec_count_cfa_sf <- c(787,5694,27214,2442,79)
vec_freq_cfa_sf <- vec_count_cfa_sf / sum(vec_count_cfa_sf)
```


```{r, include=FALSE}
(ev_cfa_sf <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cfa_sf,
                        pn_sd = n_sd_cfa_sf,
                        pvec_class_freq = vec_freq_cfa_sf,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_cfa,
                        pn_delta_mean = .1,
                        pn_gen_sd = l_gen_sd$CFa,
                        pb_verbose = TRUE))
```

###MO
```{r}
n_mean_cfa_mo <- 2.68
n_sd_cfa_mo <- 0.6
vec_count_cfa_mo <- c(373,2721,6420,280,4)
vec_freq_cfa_mo <- vec_count_cfa_mo / sum(vec_count_cfa_mo)
```


```{r, include=FALSE}
(ev_cfa_mo <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cfa_mo,
                        pn_sd = n_sd_cfa_mo,
                        pvec_class_freq = vec_freq_cfa_mo,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_cfa,
                        pn_delta_mean = .1,
                        pn_gen_sd = l_gen_sd$CFa,
                        pb_verbose = TRUE))
```



##Carcass fatness calves (CFc)
```{r}
### # prices
vec_price_cfc <- c(-1.5,
-0.6,
0.0,
-0.4,
-1.0)
```

###OB
```{r}
n_mean_cfc_ob <- 2.62
n_sd_cfc_ob <- 0.69
vec_count_cfc_ob <- c(632,2671,5379,471,3)
vec_freq_cfc_ob <- vec_count_cfc_ob / sum(vec_count_cfc_ob)
```


```{r, include=FALSE}
(ev_cfc_ob <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cfc_ob,
                        pn_sd = n_sd_cfc_ob,
                        pvec_class_freq = vec_freq_cfc_ob,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_cfc,
                        pn_delta_mean = .1,
                        pn_gen_sd = l_gen_sd$CFc,
                        pb_verbose = TRUE))
```

###BV
```{r}
n_mean_cfc_bv <- 2.68
n_sd_cfc_bv <- 0.67
vec_count_cfc_bv <- c(12790,52626,133521,11316,44)
vec_freq_cfc_bv <- vec_count_cfc_bv / sum(vec_count_cfc_bv)
```


```{r, include=FALSE}
(ev_cfc_bv <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cfc_bv,
                        pn_sd = n_sd_cfc_bv,
                        pvec_class_freq = vec_freq_cfc_bv,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_cfc,
                        pn_delta_mean = .1,
                        pn_gen_sd = l_gen_sd$CFc,
                        pb_verbose = TRUE))
```

###SI
```{r}
n_mean_cfc_si <- 2.66
n_sd_cfc_si <- 0.7
vec_count_cfc_si <- c(691,2522,5974,578,2)
vec_freq_cfc_si <- vec_count_cfc_si / sum(vec_count_cfc_si)
```


```{r, include=FALSE}
(ev_cfc_si <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cfc_si,
                        pn_sd = n_sd_cfc_si,
                        pvec_class_freq = vec_freq_cfc_si,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_cfc,
                        pn_delta_mean = .1,
                        pn_gen_sd = l_gen_sd$CFc,
                        pb_verbose = TRUE))
```

###SF
```{r}
n_mean_cfc_sf <- 2.76
n_sd_cfc_sf <- 0.65
vec_count_cfc_sf <- c(2475,11464,35025,3602,19)
vec_freq_cfc_sf <- vec_count_cfc_sf / sum(vec_count_cfc_sf)
```


```{r, include=FALSE}
(ev_cfc_sf <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cfc_sf,
                        pn_sd = n_sd_cfc_sf,
                        pvec_class_freq = vec_freq_cfc_sf,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_cfc,
                        pn_delta_mean = .1,
                        pn_gen_sd = l_gen_sd$CFc,
                        pb_verbose = TRUE))
```

###MO
```{r}
n_mean_cfc_mo <- 2.64
n_sd_cfc_mo <- 0.67
vec_count_cfc_mo <- c(191,676,1675,96,0)
vec_freq_cfc_mo <- vec_count_cfc_mo / sum(vec_count_cfc_mo)
```


```{r, include=FALSE}
(ev_cfc_mo <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cfc_mo,
                        pn_sd = n_sd_cfc_mo,
                        pvec_class_freq = vec_freq_cfc_mo,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_cfc,
                        pn_delta_mean = .1,
                        pn_gen_sd = l_gen_sd$CFc,
                        pb_verbose = TRUE))
```



##Carcass weight adults (CWa)

```{r}
 n_scale_fact_cwa <- 100
vec_price_cwa <- c(0.0,
-0.1,
-0.2,
-0.3,
-0.5,
-0.7,
-0.9,
-1.2,
-1.4,
-1.6,
-1.8)
vec_thre_cwa <- c(2.9,
3.0,
3.1,
3.2,
3.3,
3.4,
3.5,
3.6,
3.7,
3.8) * n_scale_fact_cwa
```

### OB
```{r}
n_mean_cwa_ob <- 2.61 * n_scale_fact_cwa
n_sd_cwa_ob <- 0.41 * n_scale_fact_cwa
```


```{r, include=FALSE}
(ev_cwa_ob <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cwa_ob,
                        pn_sd = n_sd_cwa_ob,
                        pvec_class_freq = NULL,
                        pvec_threshold = vec_thre_cwa,
                        pvec_price = vec_price_cwa,
                        pn_gen_sd = l_gen_sd$CWa * n_scale_fact_cwa,
                        pn_delta_mean = .01 * n_scale_fact_cwa))

```

### BV
```{r}
n_mean_cwa_bv <- 2.77 * n_scale_fact_cwa
n_sd_cwa_bv <- 0.36 * n_scale_fact_cwa
```


```{r, include=FALSE}
(ev_cwa_bv <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cwa_bv,
                        pn_sd = n_sd_cwa_bv,
                        pvec_class_freq = NULL,
                        pvec_threshold = vec_thre_cwa,
                        pvec_price = vec_price_cwa,
                        pn_gen_sd = l_gen_sd$CWa * n_scale_fact_cwa,
                        pn_delta_mean = .01 * n_scale_fact_cwa))

```


### SI
```{r}
n_mean_cwa_si <- 2.79 * n_scale_fact_cwa
n_sd_cwa_si <- 0.42 * n_scale_fact_cwa
```


```{r, include=FALSE}
(ev_cwa_si <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cwa_si,
                        pn_sd = n_sd_cwa_si,
                        pvec_class_freq = NULL,
                        pvec_threshold = vec_thre_cwa,
                        pvec_price = vec_price_cwa,
                        pn_gen_sd = l_gen_sd$CWa * n_scale_fact_cwa,
                        pn_delta_mean = .01 * n_scale_fact_cwa))

```

### SF
```{r}
n_mean_cwa_sf <- 2.88 * n_scale_fact_cwa
n_sd_cwa_sf <- 0.32 * n_scale_fact_cwa
```


```{r, include=FALSE}
(ev_cwa_sf <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cwa_sf,
                        pn_sd = n_sd_cwa_sf,
                        pvec_class_freq = NULL,
                        pvec_threshold = vec_thre_cwa,
                        pvec_price = vec_price_cwa,
                        pn_gen_sd = l_gen_sd$CWa * n_scale_fact_cwa,
                        pn_delta_mean = .01 * n_scale_fact_cwa))

```

### MO
```{r}
n_mean_cwa_mo <- 2.99 * n_scale_fact_cwa
n_sd_cwa_mo <- 0.25 * n_scale_fact_cwa
```


```{r, include=FALSE}
(ev_cwa_mo <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cwa_mo,
                        pn_sd = n_sd_cwa_mo,
                        pvec_class_freq = NULL,
                        pvec_threshold = vec_thre_cwa,
                        pvec_price = vec_price_cwa,
                        pn_gen_sd = l_gen_sd$CWa * n_scale_fact_cwa,
                        pn_delta_mean = .01 * n_scale_fact_cwa))

```



##Carcass weight calves (CWc)
```{r}
n_scale_fact_cwc <- 100
vec_price_cwc <- seq(0.0,-1.1,-0.1);vec_price_cwc
vec_thre_cwc <- seq(1.4, 1.5, 0.01) * n_scale_fact_cwc
vec_thre_cwc
```

### OB
```{r}
n_mean_cwc_ob <- 1.25 * n_scale_fact_cwc
n_sd_cwc_ob <- 0.13 * n_scale_fact_cwc
```


```{r, include=FALSE}
(ev_cwc_ob <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cwc_ob,
                        pn_sd = n_sd_cwc_ob,
                        pvec_class_freq = NULL,
                        pvec_threshold = vec_thre_cwc,
                        pvec_price = vec_price_cwc,
                        pn_gen_sd = l_gen_sd$CWc * n_scale_fact_cwc,
                        pn_delta_mean = .01 * n_scale_fact_cwc))

```

### BV
```{r}
n_mean_cwc_bv <- 1.26 * n_scale_fact_cwc
n_sd_cwc_bv <- 0.14 * n_scale_fact_cwc
```


```{r, include=FALSE}
(ev_cwc_bv <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cwc_bv,
                        pn_sd = n_sd_cwc_bv,
                        pvec_class_freq = NULL,
                        pvec_threshold = vec_thre_cwc,
                        pvec_price = vec_price_cwc,
                        pn_gen_sd = l_gen_sd$CWc * n_scale_fact_cwc,
                        pn_delta_mean = .01 * n_scale_fact_cwc))

```


### SI
```{r}
n_mean_cwc_si <- 1.27 * n_scale_fact_cwc
n_sd_cwc_si <- 0.13 * n_scale_fact_cwc
```


```{r, include=FALSE}
(ev_cwc_si <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cwc_si,
                        pn_sd = n_sd_cwc_si,
                        pvec_class_freq = NULL,
                        pvec_threshold = vec_thre_cwc,
                        pvec_price = vec_price_cwc,
                        pn_gen_sd = l_gen_sd$CWc * n_scale_fact_cwc,
                        pn_delta_mean = .01 * n_scale_fact_cwc))

```

### SF
```{r}
n_mean_cwc_sf <- 1.24 * n_scale_fact_cwc
n_sd_cwc_sf <- 0.13 * n_scale_fact_cwc
```


```{r, include=FALSE}
(ev_cwc_sf <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cwc_sf,
                        pn_sd = n_sd_cwc_sf,
                        pvec_class_freq = NULL,
                        pvec_threshold = vec_thre_cwc,
                        pvec_price = vec_price_cwc,
                        pn_gen_sd = l_gen_sd$CWc * n_scale_fact_cwc,
                        pn_delta_mean = .01 * n_scale_fact_cwc))

```

### MO
```{r}
n_mean_cwc_mo <- 1.28 * n_scale_fact_cwc
n_sd_cwc_mo <- 0.15 * n_scale_fact_cwc
```


```{r, include=FALSE}
(ev_cwc_mo <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cwc_mo,
                        pn_sd = n_sd_cwc_mo,
                        pvec_class_freq = NULL,
                        pvec_threshold = vec_thre_cwc,
                        pvec_price = vec_price_cwc,
                        pn_gen_sd = l_gen_sd$CWc * n_scale_fact_cwc,
                        pn_delta_mean = .01 * n_scale_fact_cwc))

```

## Overview of the phenotypic mean
```{r, eval=TRUE, echo=FALSE, results="asis"}
tbl_population_mean <- tibble::data_frame(Traits = c("cca", "ccc", "cfa", "cfc", "cwa", "cwc"),
                                    OB = c(n_mean_cca_ob,
                                           n_mean_ccc_ob,
                                           n_mean_cfa_ob,
                                           n_mean_cfc_ob,
                                           n_mean_cwa_ob,
                                           n_mean_cwc_ob),
                                    BV = c(n_mean_cca_bv,
                                           n_mean_ccc_bv,
                                           n_mean_cfa_bv,
                                           n_mean_cfc_bv,
                                           n_mean_cwa_bv,
                                           n_mean_cwc_bv),
                                    SI = c(n_mean_cca_si,
                                           n_mean_ccc_si,
                                           n_mean_cfa_si,
                                           n_mean_cfc_si,
                                           n_mean_cwa_si,
                                           n_mean_cwc_si),
                                    SF = c(n_mean_cca_sf,
                                           n_mean_ccc_sf,
                                           n_mean_cfa_sf,
                                           n_mean_cfc_sf,
                                           n_mean_cwa_sf,
                                           n_mean_cwc_sf),
                                    MO = c(n_mean_cca_mo,
                                           n_mean_ccc_mo,
                                           n_mean_cfa_mo,
                                           n_mean_cfc_mo,
                                           n_mean_cwa_mo,
                                           n_mean_cwc_mo))

knitr::kable(tbl_population_mean,booktabs = TRUE)
```


## Presenting output for economic values
The computed economic values are shown in the following tables:

###1.1) Table are presenting economic value in trait unit.
```{r, eval=TRUE, echo=FALSE, results="asis"}
tbl_ev_result_ev_per_trait_unit <- tibble::data_frame(Traits = c("cca", "ccc", "cfa", "cfc", "cwa", "cwc"),
                                    OB = c(ev_cca_ob$ev_per_trait_unit, 
                                            ev_ccc_ob$ev_per_trait_unit, 
                                            ev_cfa_ob$ev_per_trait_unit, 
                                            ev_cfc_ob$ev_per_trait_unit, 
                                            ev_cwa_ob$ev_per_trait_unit, 
                                            ev_cwc_ob$ev_per_trait_unit),
                                    BV = c(ev_cca_bv$ev_per_trait_unit, 
                                            ev_ccc_bv$ev_per_trait_unit, 
                                            ev_cfa_bv$ev_per_trait_unit, 
                                            ev_cfc_bv$ev_per_trait_unit, 
                                            ev_cwa_bv$ev_per_trait_unit, 
                                            ev_cwc_bv$ev_per_trait_unit),
                                    SI = c(ev_cca_si$ev_per_trait_unit, 
                                            ev_ccc_si$ev_per_trait_unit, 
                                            ev_cfa_si$ev_per_trait_unit, 
                                            ev_cfc_si$ev_per_trait_unit, 
                                            ev_cwa_si$ev_per_trait_unit, 
                                            ev_cwc_si$ev_per_trait_unit),
                                    SF = c(ev_cca_sf$ev_per_trait_unit, 
                                            ev_ccc_sf$ev_per_trait_unit, 
                                            ev_cfa_sf$ev_per_trait_unit, 
                                            ev_cfc_sf$ev_per_trait_unit, 
                                            ev_cwa_sf$ev_per_trait_unit, 
                                            ev_cwc_sf$ev_per_trait_unit),
                                    MO = c(ev_cca_mo$ev_per_trait_unit, 
                                            ev_ccc_mo$ev_per_trait_unit, 
                                            ev_cfa_mo$ev_per_trait_unit, 
                                            ev_cfc_mo$ev_per_trait_unit, 
                                            ev_cwa_mo$ev_per_trait_unit, 
                                            ev_cwc_mo$ev_per_trait_unit))

knitr::kable(tbl_ev_result_ev_per_trait_unit,booktabs = TRUE)
```

###1.2) Table are presenting economic value in genetic standard deviation.
```{r, eval=TRUE, echo=FALSE, results="asis"}
tbl_ev_result_ev_per_gen_sd <- tibble::data_frame(Traits = c("cca", "ccc", "cfa", "cfc", "cwa", "cwc"),
                                    OB = c(ev_cca_ob$ev_per_gen_sd,
                                            ev_ccc_ob$ev_per_gen_sd, 
                                            ev_cfa_ob$ev_per_gen_sd, 
                                            ev_cfc_ob$ev_per_gen_sd, 
                                            ev_cwa_ob$ev_per_gen_sd, 
                                            ev_cwc_ob$ev_per_gen_sd),
                                    BV = c(ev_cca_bv$ev_per_gen_sd, 
                                            ev_ccc_bv$ev_per_gen_sd, 
                                            ev_cfa_bv$ev_per_gen_sd, 
                                            ev_cfc_bv$ev_per_gen_sd, 
                                            ev_cwa_bv$ev_per_gen_sd, 
                                            ev_cwc_bv$ev_per_gen_sd),
                                    SI = c(ev_cca_si$ev_per_gen_sd, 
                                            ev_ccc_si$ev_per_gen_sd, 
                                            ev_cfa_si$ev_per_gen_sd, 
                                            ev_cfc_si$ev_per_gen_sd, 
                                            ev_cwa_si$ev_per_gen_sd, 
                                            ev_cwc_si$ev_per_gen_sd),
                                    SF = c(ev_cca_sf$ev_per_gen_sd, 
                                            ev_ccc_sf$ev_per_gen_sd, 
                                            ev_cfa_sf$ev_per_gen_sd, 
                                            ev_cfc_sf$ev_per_gen_sd, 
                                            ev_cwa_sf$ev_per_gen_sd, 
                                            ev_cwc_sf$ev_per_gen_sd),
                                    MO = c(ev_cca_mo$ev_per_gen_sd, 
                                            ev_ccc_mo$ev_per_gen_sd, 
                                            ev_cfa_mo$ev_per_gen_sd, 
                                            ev_cfc_mo$ev_per_gen_sd, 
                                            ev_cwa_mo$ev_per_gen_sd, 
                                            ev_cwc_mo$ev_per_gen_sd))

knitr::kable(tbl_ev_result_ev_per_gen_sd,booktabs = TRUE)
```


##2. Computing Relative Economic Factors
Relative economic factors are defined as the ratio of each economic value on the basis of one genetic standard deviation to the sum of all economic values in a given breed. The principle of how the relative economic factors are computed is shown in the chunk below. 

```{r}
tbl_ev_result_ev_per_gen_sd
# convert the tibble with economic values on the basis of one genotypic standard deviation to a matrix
mat_ev_per_gen_sd <- as.matrix(tbl_ev_result_ev_per_gen_sd[,2:ncol(tbl_ev_result_ev_per_gen_sd)])
mat_ev_per_gen_sd
# compute sum of absolute economic values within each breed
vec_abs_sum_ev <- apply(abs(mat_ev_per_gen_sd), 2, sum)
vec_abs_sum_ev
# inverse of sum
vec_inv_abs_sum_ev <- 1/vec_abs_sum_ev
vec_inv_abs_sum_ev
# extend inverse factors into a matrix
mat_inv_abs_sum_ev <- matrix(vec_inv_abs_sum_ev, nrow = nrow(mat_ev_per_gen_sd), ncol = ncol(mat_ev_per_gen_sd), byrow = TRUE)
# element-wise multiplication of matrix of economic values and matrix of inverse sums to get ratios
(mat_factors_ev <- mat_ev_per_gen_sd * mat_inv_abs_sum_ev)
mat_factors_ev
# check
apply(abs(mat_factors_ev), 2, sum)
all.equal(sum(apply(abs(mat_factors_ev), 2, sum)),ncol(mat_factors_ev))

tbl_rel_fact <- tibble::as_tibble(mat_factors_ev)
tbl_rel_fact <- bind_cols(tbl_ev_result_ev_per_gen_sd[,1],tbl_rel_fact)
```

The whole computation is now done in a function called `get_relative_economic_factors()`. This function takes as input the tibble of all economic values.
```{r, include=FALSE}
# testing function get_relative_economic _factors
class(tbl_ev_result_ev_per_gen_sd)
str(tbl_ev_result_ev_per_gen_sd[,1])
# TODO tbd: find automatic method to determine class of first column of tbl_ev_result_ev_per_gen_sd
```

###2.1) Computing Relative Economic Factors For All Categories
```{r, echo=FALSE}
### # compute factors with function
tbl_rel_factors <- MeatValueIndex::get_relative_economic_factors(ptbl_economic_value = tbl_ev_result_ev_per_gen_sd,
                                                 pb_first_col_trait_name = TRUE)
knitr::kable(tbl_rel_factors, booktabs = TRUE)
```

###2.2) Computing Relative Economic Factors For Adults
Computing the factors for different animal categories separately can be done with two separate function calls.We start with the category "addults"
```{r, echo=FALSE}
### # adults
vec_row_idx_adult <- c(1,3,5)
tbl_rel_factors_adult <- MeatValueIndex::get_relative_economic_factors(ptbl_economic_value = tbl_ev_result_ev_per_gen_sd[vec_row_idx_adult,],
                                                 pb_first_col_trait_name = TRUE)
knitr::kable(tbl_rel_factors_adult, booktabs = TRUE)
```

###2.3) Computing Relative Economic Factors For Calves
The same is done for the category "calves"
```{r, echo=FALSE}
### # adults
vec_row_idx_calves <- c(2,4,6)
tbl_rel_factors_calves <- MeatValueIndex::get_relative_economic_factors(ptbl_economic_value = tbl_ev_result_ev_per_gen_sd[vec_row_idx_calves,],
                                                 pb_first_col_trait_name = TRUE)
knitr::kable(tbl_rel_factors_calves, booktabs = TRUE)
```




##3. Importance of calves versus adults for each population
```{r, include=FALSE}
tbl_number_calves_adults <- tibble::data_frame(Categories = c("adults", "calves"),
                                    OB = c(5948,
                                           9156),
                                    BV = c(57241, 
                                          210297),
                                    SI = c(56603, 
                                           9767),
                                    SF = c(36216, 
                                           52585),
                                    MO = c(9798, 
                                           2638))

knitr::kable(tbl_number_calves_adults,booktabs = TRUE)
```

```{r, include=FALSE}
### # Proportion of the slaughtercategories for each breed
tbl_proportion <- MeatValueIndex::get_relative_economic_factors(ptbl_economic_value = tbl_number_calves_adults,
                                                                      pb_first_col_trait_name = TRUE)
```

```{r, echo=FALSE}
knitr::kable(tbl_proportion, booktabs = TRUE)
```


```{r, include=FALSE}
### # Tibble with same dimension as 'tbl_rel_factors'
(tbl_proportion4eachtrait <- bind_rows(tbl_proportion,tbl_proportion,tbl_proportion))
(tbl_proportion4eachtrait <- tbl_proportion4eachtrait[, 2:ncol(tbl_proportion4eachtrait)])
(tbl_proportion4eachtrait <- bind_cols(tbl_rel_factors[,1], tbl_proportion4eachtrait))
(colnames(tbl_proportion4eachtrait) <- colnames(tbl_rel_factors))
knitr::kable(tbl_proportion4eachtrait, booktabs = TRUE)
```


##4. Determine Relative Factors Based on Given Restrictions
animal1: normal growth
animal2: growing fast
Animal 1 and 2 have the same slaughterweight -> breeding value for animal2 is higher than animal1.
In the index, the economic value (ev) resulting of the payment system are negative for slaughterweight.

Consequence: Index animal 1 would be higher than index animal 2.

A fast solution would be according to Urs Schnyder:
ev_cwa_n = ev_cca_n

ev_cwc_n = ev_ccc_n

ev_cfa_n = alphaa * ev_cca_n

ev_cfc_n = alphac * ev_ccc_n
```{r, include=FALSE}
library(dplyr)
tbl_beta <- tibble::as_tibble(tbl_rel_fact %>% 
  filter(Traits == "ccc") %>% 
  select(OB, BV, SI, SF, MO) / 
  tbl_rel_fact %>% 
  filter(Traits == "cca") %>% 
  select(OB, BV, SI, SF, MO))
tbl_alphaa <- tibble::as_tibble(tbl_rel_fact %>% 
  filter(Traits == "cfa") %>% 
  select(OB, BV, SI, SF, MO) / 
  tbl_rel_fact %>% 
  filter(Traits == "cca") %>% 
  select(OB, BV, SI, SF, MO))
tbl_alphac <- tibble::as_tibble(tbl_rel_fact %>% 
  filter(Traits == "cfc") %>% 
  select(OB, BV, SI, SF, MO) / 
  tbl_rel_fact %>% 
  filter(Traits == "ccc") %>% 
  select(OB, BV, SI, SF, MO))

tbl_scale_factor <- bind_rows(tbl_beta, tbl_alphaa, tbl_alphac)
tbl_scale_factor
class(tbl_scale_factor)
```

Using the scale factors to compute the weights (Development of calculation should be documented)

ev_ccc_n = beta   * ev_cca_n

ev_cwa_n = 1 / (2 + 2beta + alphaa + alphac*beta)
```{r, include=FALSE}
cca_new <- tibble::as_tibble(1/(2 + 2*tbl_scale_factor[1,] + tbl_scale_factor[2,] + tbl_scale_factor[3,]*tbl_scale_factor[1,]))
cwa_new <- cca_new
ccc_new <- tibble::as_tibble(tbl_scale_factor[1,] * cca_new)
cwc_new <- ccc_new
cfa_new <- tibble::as_tibble(cca_new * tbl_scale_factor[2,])
cfc_new <- tibble::as_tibble(ccc_new * tbl_scale_factor[3,])

### # adding computed rows into a new tibble of relative factors
tbl_fact_new <- bind_rows(cca_new, ccc_new, cfa_new, cfc_new, cwa_new, cwc_new)
tbl_fact_new <- bind_cols(tibble::data_frame(Traits = c("cca", "ccc", "cfa", "cfc", "cwa", "cwc")), tbl_fact_new)
```

```{r, echo=FALSE}
knitr::kable(tbl_fact_new, booktabs = TRUE)
```


##5. Writing Output To A File
The economic values that have been computed so far are collected into a dataframe and are written to a csv-formatted file. 

Manual conversion and table1.2 output are shown below.

```{r}
vec_breed <- c("OB", "BV", "SI", "SF", "MO")
vec_trait <- c("cca", "ccc", "cfa", "cfc", "cwa", "cwc")
n_nr_trait <- length(vec_trait)

tbl_ev_input <- NULL
 for (b in vec_breed){
# b <- vec_breed[2]
  ### # put together 
  if (is.null(tbl_ev_input)){
    tbl_ev_input <- tibble::data_frame(Trait = vec_trait,
                                       Breed = rep(b, length(n_nr_trait)),
                                       Ev    = tbl_ev_result_ev_per_gen_sd[[b]])
  } else {
    tbl_ev_current <- tibble::data_frame(Trait = vec_trait,
                                       Breed = rep(b, length(n_nr_trait)),
                                       Ev    = tbl_ev_result_ev_per_gen_sd[[b]])
    tbl_ev_input <- rbind(tbl_ev_input, tbl_ev_current)
  }
    
}
readr::write_csv(tbl_ev_input, path = "ev_meat_input.csv")
```


Use the function `write_ev_to_file()`
A good initial test is to write the same tibble (table1.2) as with the manual conversion.

```{r}
MeatValueIndex::write_ev_to_file(ptbl_economic_value = tbl_ev_result_ev_per_gen_sd,
ps_out_path = "economic_value_raw.csv",
pb_first_col_trait_name = TRUE)
```

### Szenario A) we are using the relative economic factors (table 2.1)

```{r}
MeatValueIndex::write_ev_to_file(ptbl_economic_value = tbl_rel_factors,
                                 ps_out_path = "economic_value_relative.csv",
                                 pb_first_col_trait_name = TRUE)
```

### Szenario B) The relative factors are weighted with animal categories to get weighted relative factors

```{r}
tbl_weighted_rel_factors <- MeatValueIndex::weight_economic_value(ptbl_economic_value = tbl_rel_factors,
                                     ptbl_weight = tbl_proportion4eachtrait,
                                     pb_first_col_trait_name = TRUE)
# tbl_weighted_rel_factors
MeatValueIndex::write_ev_to_file(ptbl_economic_value = tbl_weighted_rel_factors,
                                ps_out_path = "weighted_economic_value_relative.csv",
                                pb_first_col_trait_name = TRUE)
```

### Szenario C) This set consist of the creative political values not weighted for animal classes (table 4)

```{r}
MeatValueIndex::write_ev_to_file(ptbl_economic_value = tbl_fact_new, 
                                  ps_out_path = "political_unweighted.csv",
                                 pb_first_col_trait_name = TRUE)
```

### Szenario D) The last set is the above factors weighted with the proportions of the animal classes

```{r}
tbl_weighted_fact_new <- MeatValueIndex::weight_economic_value(ptbl_economic_value = tbl_fact_new,
                                     ptbl_weight = tbl_proportion4eachtrait,
                                     pb_first_col_trait_name = TRUE)
MeatValueIndex::write_ev_to_file(ptbl_economic_value = tbl_weighted_fact_new,
                                ps_out_path = "political_weighted.csv",
                                pb_first_col_trait_name = TRUE)

```
