---
title: "Testing Function To Compute Economic Values"
output: html_notebook
---


## Disclaimer
The package `MeatValueIndex` contains the function `compute_economic_value()` to compute economic values for a variety of traits. We want to validate this function with calculations that were made during the MSc of Silvan Wyss. In what follows, we compute economic values for a given trait within a certain breed using both methods and compare the results.


## CCa for AN

First, we start with specifying the information that is constant for the trait CCa for all breeds. This consists of the vector of the prices in the slaughterhouse.

```{r}
### # prices
vec_price_cca <- c(7.526960,7.938872,8.450784,8.800000,9.137304,9.392693,9.642693)
vec_price_ccc <- c(11.2,12.7,13.6,14.2,14.7,15.2,15.7)
```

Next, we indicate all information that is specific for the breed AN.

```{r}
n_mean_cca_an <- 5.62
n_sd_cca_an <- 1
vec_freq_cca_an <- c(0.000000000,
0.000637062, 
0.009256136, 
0.129623384, 
0.311335957, 
0.331909312, 
0.217238149)
(ev_cca_an <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cca_an,
                        pn_sd = n_sd_cca_an,
                        pvec_class_freq = vec_freq_cca_an,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_cca,
                        pn_delta_mean = .1))
```


## CCc for AN
```{r}
n_mean_ccc_an <- 5.48
n_sd_ccc_an <- 0.99
vec_freq_ccc_an <- c(0.001021972,
                     0.001021972,
                     0.017884517,
                     0.142054165,
                     0.323965253,
                     0.361778232,
                     0.152273889)
(ev_ccc_an <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_ccc_an,
                        pn_sd = n_sd_ccc_an,
                        pvec_class_freq = vec_freq_ccc_an,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_ccc,
                        pn_delta_mean = .1))
```


## CFa for AN

Prices for CFa

```{r}
vec_price_cfa <- c(-0.9000000,
-0.3000000,
0.0000000,
-0.3926929,
-0.8480817)
vec_price_cfc <- c(-1.5,
-0.6,
0.0,
-0.4,
-1.0)
```


```{r}
n_mean_cfa_an <- 3.08
n_sd_cfa_an <- 0.74
vec_freq_cfa_an <- c(0.03005434,
0.12797452,
0.58733371,
0.23661233,
0.01802511)
(ev_cfa_an <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cfa_an,
                        pn_sd = n_sd_cfa_an,
                        pvec_class_freq = vec_freq_cfa_an,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_cfa,
                        pn_delta_mean = .1))

```

## CFc for AN
```{r}
n_mean_cfc_an <- 2.51
n_sd_cfc_an <- 0.76
vec_freq_cfc_an <- c(0.096576392,
0.360756260,
0.477772100,
0.063873275,
0.001021972)
(ev_cfc_an <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cfc_an,
                        pn_sd = n_sd_cfc_an,
                        pvec_class_freq = vec_freq_cfc_an,
                        pvec_threshold = NULL,
                        pvec_price = vec_price_cfc,
                        pn_delta_mean = .1))
```


## CWa for AN
The CW traits are continuous which leads to the use of a different computational method. This is not visible from the outside, but is driven only by the input parameters

```{r}
n_scale_fact_cwa_an <- 100
n_mean_cwa_an <- 2.32 * n_scale_fact_cwa_an
n_sd_cwa_an <- 0.53 * n_scale_fact_cwa_an
vec_price_cwa <- c(0.0,
-0.1,
-0.2,
-0.3,
-0.5,
-0.7,
-0.9,
-1.2,
-1.4,
-1.6,
-1.8)
vec_thre_cwa <- c(2.9,
3.0,
3.1,
3.2,
3.3,
3.4,
3.5,
3.6,
3.7,
3.8) * n_scale_fact_cwa_an

(ev_cwa_an <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cwa_an,
                        pn_sd = n_sd_cwa_an,
                        pvec_class_freq = NULL,
                        pvec_threshold = vec_thre_cwa,
                        pvec_price = vec_price_cwa,
                        pn_delta_mean = .01 * n_scale_fact_cwa_an))
```


## CWc for AN

```{r}
n_scale_fact_cwc_an <- 100
n_mean_cwc_an <- 1.23 * n_scale_fact_cwc_an
n_sd_cwc_ad <- 0.14 * n_scale_fact_cwc_an
vec_price_cwc <- c(0.0,
-0.1)
vec_thre_cwc <- 1.4 * n_scale_fact_cwc_an
(ev_cwc_an <- MeatValueIndex::compute_economic_value( pn_mean = n_mean_cwc_an,
                        pn_sd = n_sd_cwc_ad,
                        pvec_class_freq = NULL,
                        pvec_threshold = vec_thre_cwc,
                        pvec_price = vec_price_cwc,
                        pn_delta_mean = .01 * n_scale_fact_cwc_an))
```


