---
title: "Weighting Strategies"
output: html_notebook
---


## Disclaimer
This notebook gives an overview over different weighting strategies between economic values of traits of different animal categories.


## Background
In beef cattle there are three different carcass performance traits. 

```{r traittable, echo=FALSE, results='asis'}
tbl_trait <- tibble::data_frame(Abbreviation = c("CC", "CF", "CW"),
                                Trait = c("Carcass Conformation",
                                          "Carcass Fat",
                                          "Carcass Weight"))
knitr::kable( tbl_trait,
              booktabs = TRUE,
              longtable = TRUE )
```


Both traits are available in two animal categories

```{r categorytable, echo=FALSE, results='asis'}
tbl_category <- tibble::data_frame(Abbreviation = c("c", "a"),
                                   Category     = c("calf", "adult"))
knitr::kable( tbl_category,
              booktabs = TRUE,
              longtable = TRUE )
```


```{r computenrtrait, echo=FALSE, results='hide'}
n_nr_trait <- nrow(tbl_category) * nrow(tbl_trait)
```

Combining both, results in the following matrix of a total of `r n_nr_trait` traits

```{r traitmatrix, echo=FALSE, results='asis'}
tbl_trait_matrix <- tibble::data_frame(Trait = c("CC", "CF", "CW"),
                                       Calf  = c("CCc", "CFc", "CWc"),
                                       Adult = c("CCa", "CFa", "CWa"))
knitr::kable( tbl_trait_matrix,
              booktabs = TRUE,
              longtable = TRUE )
```


## Economic Values
Economic values for all `r n_nr_trait` traits were computed using a simplified profit function leading to the following results.

```{r economicvalues, echo=FALSE, results='asis'}
tbl_economic_value <- tibble::data_frame(Trait = c(("CCa", "CFa", "CWa")))
```

